---
# title: "**Pelagics**"
# subtitle: "Operating Model Figures"
# author: "L Kell"
# date: "`r format(Sys.time(), '%d %B, %Y')`"
# output: html_document
output:
  html_document:
    reference_docx: ../report_template.dotx
mathjax: TRUE
# fig_width: 6 
# fig_height: 4 
# tags: FLR FLCore introduction
# license: Creative Commons Attribution-ShareAlike 4.0 International Public License
# bibliography: refs.bib
---

# Results

The effect of 

```{r, knitr, eval=TRUE, echo=FALSE, warning=FALSE}
library(knitr)

knitr::opts_chunk$set(
               cache     =TRUE, 
               comment   ="", 
               warning   =FALSE, 
               message   =FALSE, 
               error     =FALSE, 
               echo      =FALSE, 
               eval      =TRUE,
               crop      =TRUE,
               cache.path="../cache/figs/finalFigs/",
               fig.path  ="../tex/figs/",
               fig.width =10,
               fig.height=6,
               dev       ="png")

iFig=0
iTab=0
nits=100

```


```{r, pkgs}
library(FLCore) 
library(ggplotFL)
library(FLfse)
library(FLBRP)
library(FLasher)
library(FLAssess)
library(FLSAM)
library(kobe)   
library(mpb)    

library(rjson) # install.packages("rjson"); used for dropbox function
library(RJSONIO)

library(TMB)
library(stockassessment)
  
library(plyr)
library(dplyr)
library(reshape)
library(magrittr)
library(ggpubr)
  
library(grid) 
library(ggpubr)

library(compositions) 

theme_set(theme_bw(16))
```

```{r, source}
source('../R/kobe-phaseMar.R')
source('../R/kobe-phase.R')
source('../R/get_dropbox.r')
source("../R/pm.R")
```


```{r, dbox}
dropboxdir<-try(file.path(get_dropbox(), "pelagics"))

if ("try-error"%in%is(dropboxdir))
  dropboxdir="~/Dropbox/pelagics"
```



```{r, source2}

# Projection function

prj<-function(x,
              ftar,
              yrs=dimnames(x)$year[dim(m(x))[2]-31:0],
              nit=nits){
  f0=array(c(rep(c(1,rep(0,dim(x)[1])),dim(x)[1]-1),1),
           c(dim(harvest(x))[1],dim(harvest(x))[1]),
           dimnames=list(dims(x)$min:dims(x)$max,dims(x)$min:dims(x)$max))
  f0=f0*0.05
  F0=aperm(maply(data.frame(year=yrs), function(year) rlnorm.rplus(nits,rep(0,dim(x)[1]),f0)),c(3,1,2)) 
  names(dimnames(F0))[c(1,3)]=c("age","iter")
  F0=as.FLQuant(c(F0),dimnames=dimnames(F0))
  
  x=propagate(x,nit)
  stock.n(x)[,ac(yrs)]=stock.n(x)[,ac(yrs)]%*%F0
  
  control=as(FLQuants("f"=ftar),"fwdControl")
  
  res=fwd(x,sr=rec(x),control=control)
  res
}

# load(file.path(dropboxdir, "data/inputs/MAC/model fit.RData"))

sam2FLQuant<-function(x,row=1){
  FLQuants(ssb     =
             FLQuant(x[["sdrep"]][[row]][names(x[["sdrep"]][["value"]])=="logssb"], 
                     dimnames=list(year=x[["data"]][["years"]])),
           fbar    =
             FLQuant(x[["sdrep"]][[row]][names(x[["sdrep"]][["value"]])=="logfbar"],  
                     dimnames=list(year=x[["data"]][["years"]])),
           catch   =
             FLQuant(x[["sdrep"]][[row]][names(x[["sdrep"]][["value"]])=="logCatch"], 
                     dimnames=list(year=x[["data"]][["years"]])),
           landings=
             FLQuant(x[["sdrep"]][[row]][names(x[["sdrep"]][["value"]])=="logLand"],  
                     dimnames=list(year=x[["data"]][["years"]])),
           rec     =
             FLQuant(x[["sdrep"]][[row]][names(x[["sdrep"]][["value"]])=="logR"],     
                     dimnames=list(year=x[["data"]][["years"]])),
           biomass =
             FLQuant(x[["sdrep"]][[row]][names(x[["sdrep"]][["value"]])=="logtsb"],   
                     dimnames=list(year=x[["data"]][["years"]])))}

```

```{r, load}
load(file.path(dropboxdir, "data/om/whb.RData"))
load(file.path(dropboxdir, "data/om/her.RData"))
load(file.path(dropboxdir, "data/om/mac.RData"))
load(file.path(dropboxdir, "data/om/whbRet.RData"))
load(file.path(dropboxdir, "data/om/herRet.RData"))
load(file.path(dropboxdir, "data/om/macRet.RData"))
load(file.path(dropboxdir, "data/om/whbErr.RData"))
load(file.path(dropboxdir, "data/om/herErr.RData"))
load(file.path(dropboxdir, "data/om/macErr.RData"))

refs=read.csv(file.path(dropboxdir,"data/inputs/refs.csv"),header=T)
refs=melt(refs,measure=c("flim","fpa","fmsy","fcap","blim","bpa","msybtrigger"),id=c("spp","assessmentyear"))
refs=transmute(refs,spp=spp,year=an(assessmentyear),ref=variable,data=an(value))
refs=merge(refs,data.frame(ref=unique(refs$ref),qname=c(rep("F",4),rep("SSB",3))))
```

\newpage
```{r, assessment, warning=FALSE}
assessment =list() 

assessment[["whb"]] <-
  ggplotFL::plot(window(whb, 1990))+  
  
  geom_line(data = filter(refs, 
                          spp=="Blue whiting" & 
                          ref %in%c("blim","bpa","msybtrigger", "fmsy", "fpa")),
            aes(year, data, col=ref)) +
  theme(legend.position="bottom")+
  scale_color_manual("Reference\nPoints",values=rainbow(7))

assessment[["her"]] <-
  plot(window(her, 1990))+  
  geom_line(data = filter(refs, 
                          spp=="Herring" & 
                          ref %in%c("blim","bpa","msybtrigger", "fmsy", "fpa")),
            aes(year, data, col=ref)) +
  #scale_color_manual(values=c("red","blue"))+
  theme(legend.position="bottom")+
  scale_color_manual("Reference\nPoints",values=rainbow(7))

assessment[["mac"]] <- 
  plot(window(mac, 1990))+  
  geom_line(data = filter(refs, 
                          spp=="Mackerel" & 
                          ref %in%c("blim","bpa","msybtrigger", "fmsy", "fpa")),
            aes(year, data, col=ref)) +
  #scale_color_manual(values=c("red","blue"))+
  theme(legend.position="bottom")+
  scale_color_manual("Reference\nPoints",values=rainbow(7))

# plot together

ggarrange(
  assessment[["whb"]]+theme_bw()+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)),
          
  assessment[["her"]]+theme_bw()+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)),
          
  assessment[["mac"]]+theme_bw()+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)), 
          nrow = 1,ncol=3,
          common.legend=TRUE, legend = "bottom",
          labels = c("WHB","HER","MAC"))
```

**Figure `r iFig=iFig+1;iFig`** Most recent ICES assessments with F and SSB reference points

\newpage

```{r refs, fig.asp=0.6, warning=FALSE}
refplots <- list()

refplots[["f"]] <-
  refs %>% 
  filter(ref %in% c("fpa", "fmsy", "flim")) %>%
  mutate(ref = gsub("f","", ref)) %>% 
  mutate(ref = factor(ref, levels=c("lim","pa", "msy"))) %>% 
  dplyr::rename(variable = qname) %>% 
  
  ggplot()+
  geom_line( aes(year,as.numeric(data),colour=ref))+
  geom_point(aes(year,as.numeric(data),colour=ref))+
  labs(x="", y="") +
  expand_limits(y=0) +
  facet_grid(spp~variable,scale="free")+
  scale_colour_manual(values=c("red","orange","green"))

refplots[["ssb"]] <-
  refs %>% 
  filter(ref %in% c("blim","bpa","msybtrigger")) %>% 
  mutate(ref = gsub("^b","", ref)) %>% 
  mutate(ref = gsub("btrigger","", ref)) %>% 
  mutate(ref = factor(ref, levels=c("lim","pa", "msy"))) %>% 
  dplyr::rename(variable = qname) %>% 
  
  ggplot()+
  geom_line( aes(year,as.numeric(data),colour=ref))+
  geom_point(aes(year,as.numeric(data),colour=ref))+
  labs(x="", y="") +
  expand_limits(y=0) +
  facet_grid(spp~variable,scale="free")+
  scale_colour_manual(values=c("red","orange","green"))


ggarrange(
  refplots[["ssb"]]+theme_bw()+
  theme(panel.grid.major =element_blank(),
        strip.background.y = element_blank(), strip.text.y = element_blank(),
        text = element_text(size = 16),
        # axis.ticks       =element_blank(),
        # axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)),
          
  refplots[["f"]]+theme_bw()+
  theme(panel.grid.major =element_blank(),
        text = element_text(size = 16),
        # axis.ticks       =element_blank(),
        # axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)), 
          
  nrow = 1,ncol=2,
  common.legend=TRUE, legend = "bottom")
```

**Figure `r iFig=iFig+1;iFig`** ICES SSB and Fishing Mortality reference points, as estimated at each benchmark assessment.

```{r, vpa}
load(file.path(dropboxdir,"data/om/whbVPA.RData"))
load(file.path(dropboxdir,"data/om/herVPA.RData"))
load(file.path(dropboxdir,"data/om/macVPA.RData"))

ggarrange(
  whbVPA+theme_bw()+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA))+
  expand_limits(y=0),

  herVPA+theme_bw()+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)) +
  expand_limits(y=0),
          
  macVPA+theme_bw()+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA))+
  expand_limits(y=0),
  
  nrow = 1,ncol=3,
  common.legend=TRUE, legend="none",
  labels = c("WHB","HER","MAC"), 
  label.x = rep(0.06,3),
  label.y = rep(0.99,3)) 
```

**Figure `r iFig=iFig+1;iFig`** VPAs. 

```{r}
load(file.path(dropboxdir,"data/om/proj.RData"))

ggarrange(
  proj[["whb"]]+theme_bw()+scale_color_manual(values=c("black","blue","red"))+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA))+
  expand_limits(y=0),

  proj[["her"]]+theme_bw()+scale_color_manual(values=c("black","blue","red"))+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)) +
  expand_limits(y=0),
          
  proj[["mac"]]+theme_bw()+scale_color_manual(values=c("black","blue","red"))+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA))+
  expand_limits(y=0),
  
  nrow = 1,ncol=3,
  common.legend=TRUE, legend="none",
  labels = c("WHB","HER","MAC"), 
  label.x = rep(0.06,3),
  label.y = rep(0.99,3)) 
```


**Figure `r iFig=iFig+1;iFig`** References 

\newpage
## Retrospective analyses

```{r, retro, warning=FALSE, fig.asp=1.0}
retros=list("whb"=plot(window(whbRet,start=1990),metrics=list("SSB"=ssb,"F"=fbar, "rec"=rec))+
  theme_bw()+ 
  theme(legend.position="none"))

# retros[["whb"]]

retros[["her"]]=
  plot(
    window(herRet,start=1990),
    metrics=list("SSB"=ssb,"F"=fbar, "rec"=rec)
  )+
  theme_bw()+ 
  theme(legend.position="none") 

# retros[["her"]]

retros[["mac"]]=plot(window(macRet,start=1990),metrics=list("SSB"=ssb,"F"=fbar, "rec"=rec))+
  theme_bw()+ 
  theme(legend.position="none")

# retros[["mac"]]+facet_grid(.~qname)

ggarrange(
  retros[["whb"]]+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA))+
  expand_limits(y=0),

  retros[["her"]]+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)) +
  expand_limits(y=0),
          
  retros[["mac"]]+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA))+
  expand_limits(y=0),
  
  nrow = 1,ncol=3,
  common.legend=TRUE, legend="none",
  labels = c("WHB","HER","MAC"), 
  label.x = rep(0.06,3),
  label.y = rep(0.99,3)) 
```

**Figure `r iFig=7;iFig`** Retrospective analysis for ICES assessments. 


## Assessment Error

```{r, kobe-err, fig.height=8, fig.width=8, warning=FALSE}
# library(grid) 

dt=as.data.frame(rmvnorm(1000,c(1,1),cov(whbErr[-1,])))
names(dt)=c("stock","harvest")
kobePhaseMar(dt,quadcol=c("white","white","white","white"), xlab="F",ylab="SSB")

dt=as.data.frame(rmvnorm(1000,c(1,1),cov(herErr[-1,])))
names(dt)=c("stock","harvest")
kobePhaseMar(dt,quadcol=c("white","white","white","white"), xlab="F",ylab="SSB")

dt=as.data.frame(rmvnorm(1000,c(1,1),cov(macErr[-1,])))
names(dt)=c("stock","harvest")
kobePhaseMar(dt,quadcol=c("white","white","white","white"), xlab="F",ylab="SSB")

# ggarrange stuff here

```

**Figure `r iFig=iFig+1;iFig`** Blue whiting, Herring and Mackerel: assessment error


\newpage

## Harvest control rules


```{r, load-runs}
load(file.path(dropboxdir,"data/runs/whb.RData"));whb=sims 
load(file.path(dropboxdir,"data/runs/her.RData"));her=sims 
load(file.path(dropboxdir,"data/runs/mac.RData"));mac=sims 
```

```{r, theme}
theme_pelac<-function() { 
  theme(
    # add border 1)
    panel.border = element_rect(colour = "blue", fill = NA, linetype = 1),
    # color background 2)
    panel.background = element_rect(fill = "white"),
    # modify grid 3)
    panel.grid.major.x = element_line(colour = "steelblue", linetype = 3, size = 0.5),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    # modify text, axis and colour 4) and 5)
    axis.text.x= element_text(colour = "steelblue", face = "italic", family = "Times New Roman"),
    axis.text.y= element_blank(),
    axis.title = element_text(colour = "steelblue", family = "Times New Roman"),
    axis.ticks = element_line(colour = "steelblue"),
    # legend at the bottom 6)
    legend.position = "bottom")
    }

```

```{r, reference, fig.asp=0.75}
what=c("ICES","Fmsy") 
p1=plot(FLStocks(llply(whb[what], function(x) x[[1]])))+theme_pelac()
p2=plot(FLStocks(llply(her[what], function(x) x[[1]])))+theme_pelac()
p3=plot(FLStocks(llply(mac[what], function(x) x[[1]])))+theme_pelac()

ggarrange(p1,p2,p3, 
          nrow = 1,ncol=3,
          common.legend=TRUE, legend = "bottom",
          labels = c("WHB","HER","MAC"), label.x=0.05, label.y=0.05)
```
**Figure `r iFig=iFig+1;iFig`** Blue whiting, Herring and Mackerel: Reference cases

```{r}
whbVPA+theme_bw()
```
**Figure `r iFig=iFig;iFig`a** Blue whiting VPA reconstruction

```{r}
herVPA+theme_bw()
```
**Figure `r iFig=iFig;iFig`b** Herring VPA reconstruction

```{r}
macVPA+theme_bw()
```
**Figure `r iFig=iFig;iFig`c** Mackerel VPA reconstruction

```{r}
p<-function(what,stks=list(whb=whb,her=her,mac=mac)){
    
  plt=llply(stks, function(x) 
    plot(FLStocks(llply(x[what], function(y)y[[1]])),
                     metrics=list(SSB=ssb,Catch=catch,F=fbar))+
    theme_pelac()+
    scale_x_continuous(limits=c(1990,2021)))
  
  plt=ggarrange(plt[[1]],plt[[2]],plt[[3]], 
            nrow = 1,ncol=3,
            common.legend=TRUE, legend = "bottom",
            labels = c("WHB","HER","MAC"), label.x=0.05, label.y=0.05)
  #print(plt)
  plt}
```

```{r, hcr, fig.asp=0.75}
p(c("ICES","HCR1","HCR2"))
```
**Figure `r iFig=10; iFig`** Blue whiting, Herring and Mackerel: HCRs

```{r, hcr-bnd, fig.asp=0.75}
p(c("ICES","HCR1 bnd","HCR2 bnd"))
```
**Figure `r iFig=iFig+1;iFig`** Blue whiting, Herring and Mackerel: HCRs with bounds


```{r,  hcr-bn-cap, fig.asp=0.75}
p(what=c("ICES", "HCR1 bnd cap","HCR2 bnd cap"))
```
**Figure `r iFig=iFig+1;iFig`** Blue whiting, Herring and Mackerel: HCRS with Bounds and cap


```{r, impErr, fig.asp=0.75}
p(what=c("ICES","HCR1","HCR1 +10%","HCR1 +20%","HCR1 +30%"))
```
**Figure `r iFig=iFig+1;iFig`** Blue whiting, Herring and Mackerel: HCRS with Bounds and implementation error


```{r, impErr-recent, fig.asp=0.75}
p(what=c("ICES","HCR1","HCR1 +10% recent","HCR1 +20% recent","HCR1 +30% recent"))
```
**Figure `r iFig=iFig+1;iFig`** Blue whiting, Herring and Mackerel: HCRS with Bounds and implementation error

```{r, impErr-bnd, fig.asp=0.75}
p(what=c("ICES","HCR1","HCR1 +10% bnd","HCR1 +20% bnd","HCR1 +30% bnd"))
```
**Figure `r iFig=iFig+1;iFig`** Blue whiting, Herring and Mackerel: HCRS with Bounds and implementation error

```{r, impErr-bnd-recent, fig.asp=0.75}
p(what=c("ICES","HCR1","HCR1 +10% bnd recent","HCR1 +20% bnd recent","HCR1 +30% bnd recent"))
```
**Figure `r iFig=iFig+1;iFig`** Blue whiting, Herring and Mackerel: HCRS with Bounds and implementation error

```{r, impErr-bnd-recent2, fig.asp=0.75}
p(what=c("ICES","HCR1","HCR1 +10% bnd recent","HCR1 +20% bnd recent","HCR1 +30% bnd recent"))
```
**Figure `r iFig=iFig+1;iFig`** Blue whiting, Herring and Mackerel: HCRS with Bounds and implementation error in last 10 years


```{r, impErr-30, fig.asp=0.75}
p(what=c("ICES","HCR2","HCR2 +30% bnd","HCR2 +30% bnd recent")[-4])
```
**Figure `r iFig=iFig+1;iFig`** Blue whiting, Herring and Mackerel: HCRS with Bounds and implementation error in last 10 years


```{r, impErr-30-2, fig.asp=0.75}
p(what=c("ICES","HCR2","HCR2 +30% bnd","HCR2 +30% bnd recent")[-4])
```
**Figure `r iFig=iFig+1;iFig`** Blue whiting, Herring and Mackerel: HCRS with Bounds and implementation error in last 10 years


```{r, chk, fig.asp=0.75}
p(what=c("HCR1 bnd","HCR1 +10% bnd","HCR1 +10% bnd recent"))
```
**Figure `r iFig=iFig+1;iFig`** Blue whiting, Herring and Mackerel: HCRS with Bounds and 30% implementation error in last 10 years


# Funding

# References
