---
# title: "**Pelagics**"
# subtitle: "Operating Model Conditioning"
# author: "L Kell"
# date: "`r format(Sys.time(), '%d %B, %Y')`"
# output: html_document
output:
  word_document:
    reference_docx: ../report_template.dotx
mathjax: TRUE
# fig_width: 6 
# fig_height: 4 
# tags: FLR FLCore introduction
# license: Creative Commons Attribution-ShareAlike 4.0 International Public License
# bibliography: refs.bib
---


```{r, knitr, eval=TRUE, echo=FALSE, warning=FALSE}
library(knitr)

knitr::opts_chunk$set(
               cache     =TRUE, 
               comment   ="", 
               warning   =FALSE, 
               message   =FALSE, 
               error     =FALSE, 
               echo      =FALSE, 
               eval      =TRUE,
               crop      =TRUE,
               cache.path="../cache/figs/cond/",
               fig.path  ="../tex/figs",
               fig.width =10,
               fig.height=8,
               dev       ="png")

iFig=0
iTab=0
nits=100

```


```{r, pkgs}
# install.packages("FLBRP", repos="http://flr-project.org/R")
# install.packages("FLasher", repos="http://flr-project.org/R")
# install.packages("FLAssess", repos="http://flr-project.org/R")
# remotes::install_github('fishfollower/SAM/stockassessment', ref='components')
# remotes::install_github("flr/FLSAM")
# remotes::install_github("flr/kobe")
# remotes::install_github("flr/FLfse/FLfse")
# remotes::install_github("lauriekell/mpb")
# install.packages("compositions")

library(FLCore) 
library(ggplotFL)
library(FLfse)
library(FLBRP)
library(FLasher)
library(FLAssess)
library(FLSAM)
library(kobe)   
library(mpb)    

library(rjson) # install.packages("rjson"); used for dropbox function
library(RJSONIO)

library(TMB)
library(stockassessment)
  
library(plyr)
library(dplyr)
library(reshape)
library(magrittr)
library(ggpubr)
  
library(grid) 
library(ggpubr)

library(compositions) 


theme_set(theme_bw(16))
```

```{r, source}
source('../R/kobe-phaseMar.R')
source('../R/kobe-phase.R')
source('../R/get_dropbox.r')
source("../R/pm.R")

```


```{r, dbox}
dropboxdir<-try(file.path(get_dropbox(), "pelagics"))

if ("try-error"%in%is(dropboxdir))
  dropboxdir="~/Dropbox/pelagics"
```


```{r, source2}

# Projection function

prj<-function(x,
              ftar,
              yrs=dimnames(x)$year[dim(m(x))[2]-31:0],
              nit=nits){
  f0=array(c(rep(c(1,rep(0,dim(x)[1])),dim(x)[1]-1),1),
           c(dim(harvest(x))[1],dim(harvest(x))[1]),
           dimnames=list(dims(x)$min:dims(x)$max,dims(x)$min:dims(x)$max))
  f0=f0*0.05
  F0=aperm(maply(data.frame(year=yrs), function(year) rlnorm.rplus(nits,rep(0,dim(x)[1]),f0)),c(3,1,2)) 
  names(dimnames(F0))[c(1,3)]=c("age","iter")
  F0=as.FLQuant(c(F0),dimnames=dimnames(F0))
  
  x=propagate(x,nit)
  stock.n(x)[,ac(yrs)]=stock.n(x)[,ac(yrs)]%*%F0
  
  control=as(FLQuants("f"=ftar),"fwdControl")
  
  res=fwd(x,sr=rec(x),control=control)
  res
}

# load(file.path(dropboxdir, "data/inputs/MAC/model fit.RData"))

sam2FLQuant<-function(x,row=1){
  FLQuants(ssb     =
             FLQuant(x[["sdrep"]][[row]][names(x[["sdrep"]][["value"]])=="logssb"], 
                     dimnames=list(year=x[["data"]][["years"]])),
           fbar    =
             FLQuant(x[["sdrep"]][[row]][names(x[["sdrep"]][["value"]])=="logfbar"],  
                     dimnames=list(year=x[["data"]][["years"]])),
           catch   =
             FLQuant(x[["sdrep"]][[row]][names(x[["sdrep"]][["value"]])=="logCatch"], 
                     dimnames=list(year=x[["data"]][["years"]])),
           landings=
             FLQuant(x[["sdrep"]][[row]][names(x[["sdrep"]][["value"]])=="logLand"],  
                     dimnames=list(year=x[["data"]][["years"]])),
           rec     =
             FLQuant(x[["sdrep"]][[row]][names(x[["sdrep"]][["value"]])=="logR"],     
                     dimnames=list(year=x[["data"]][["years"]])),
           biomass =
             FLQuant(x[["sdrep"]][[row]][names(x[["sdrep"]][["value"]])=="logtsb"],   
                     dimnames=list(year=x[["data"]][["years"]])))}

```

```{r, assessment-whb}
load(file.path(dropboxdir, "data/inputs/WHB/run/model.RData"))

whb=SAM2FLStock(fit)
whbR=FLBRP(whb,nyears=20)
params(whbR)[]=median(rec(whb))

catch(whb)=computeCatch(whb,"all")

# save(whb,whbR,file=file.path(dropboxdir, "data/om/whb.RData"))
```

```{r, assessment-her}
load(file.path(dropboxdir, "data/inputs/HER/NSAS_HAWG2022_sf.RData"))

her=NSH
herR=FLBRP(her,nyears=20)
params(herR)[]=median(rec(her))

catch(her)=computeCatch(her,"all")

save(her,herR,file=file.path(dropboxdir, "data/om/her.RData"))
```

```{r, assessment-mac}
load(file.path(dropboxdir, "data/inputs/MAC/model fit.RData"))

mac =SAM2FLStock(fit.new)
mac=window(mac,end=2021)
macR=FLBRP(mac,nyears=20)
params(macR)[]=median(rec(mac))

catch(mac)=computeCatch(mac,"all")

# save(mac,macR,file=file.path(dropboxdir, "data/om/mac.RData"))
```



```{r, retro-whb}
load(file.path(dropboxdir, "data/inputs/WHB/run/retro.RData"))
whbRet=FLStocks(llply(RETRO, SAM2FLStock))
names(whbRet)=laply(whbRet, function(x) dims(x)$maxyear)
# save(whbRet,file=file.path(dropboxdir, "data/om/whbRet.RData"))

```

```{r, retro-her}
load(file.path(dropboxdir, "data/inputs/HER/NSAS_HAWG2022_sf_retro.RData"))
load(file.path(dropboxdir, "data/om/her.RData"))
herRet=FLStocks(llply(NSH.retro, function(x) {
  res         =window(her,end=dims(x)$maxyear)
  stock.n(res)=stock.n(x)
  harvest(res)=harvest(x)
  res}))
names(herRet)=laply(herRet, function(x) dims(x)$maxyear)
# save(herRet,file=file.path(dropboxdir, "data/om/herRet.RData"))

```

```{r, retro-mac}
load(file.path(dropboxdir, "data/inputs/MAC/retro.RData"))
macRet=FLStocks(llply(ret,SAM2FLStock))
names(macRet)=laply(macRet, function(x) dims(x)$maxyear)
# save(macRet,file=file.path(dropboxdir, "data/om/macRet.RData"))
```


```{r, whbErr}
load(file.path(dropboxdir, "data/om/whbRet.RData"))

om1=whbRet[[1]]
whbErr=laply(whbRet, function(x){
  yr=ac(dims(fbar(x))$maxyear)
  
  c(f  =c(fbar(x)[,yr]/fbar(om1)[,yr]),
    ssb=c(ssb(x)[,yr])/c(ssb(om1)[,yr]))})

# save(whbErr,file=file.path(dropboxdir, "data/om/whbErr.RData"))
```

```{r, herErr}
# load("../data/inputs/HER/NSAS_HAWG2022_sf.RData")
load(file.path(dropboxdir, "data/om/herRet.RData"))

om1=herRet[[1]]
herErr=laply(herRet, function(x){
  yr=ac(dims(fbar(x))$maxyear)
  
  c(f  =c(fbar(x)[,yr]/fbar(om1)[,yr]),
    ssb=c(ssb(x)[,yr])/c(ssb(om1)[,yr]))})

save(herErr,file=file.path(dropboxdir, "data/om/herErr.RData"))
# # save(herErr, file="../data/om/herErr.RData")
```

```{r, macErr}
load(file.path(dropboxdir, "data/om/macRet.RData"))
# load("../data/om/macRet.RData")

om1=macRet[[1]]
macErr=laply(macRet, function(x){
  yr=ac(dims(fbar(x))$maxyear)
  
  c(f  =c(fbar(x)[,yr]/fbar(om1)[,yr]),
    ssb=c(ssb(x)[,yr])/c(ssb(om1)[,yr]))})

# save(macErr,file=file.path(dropboxdir, "data/om/macErr.RData"))
# save(macErr, file="../data/om/macErr.RData")
```

```{r, data}
load(file.path(dropboxdir,"data/om/whb.RData"))
load(file.path(dropboxdir,"data/om/her.RData"))
load(file.path(dropboxdir,"data/om/mac.RData")) 

refs=read.csv(file.path(dropboxdir,"data/inputs/refs.csv"),header=T)
refs=melt(refs,measure=c("flim","fpa","fmsy","fcap","blim","bpa","msybtrigger"),id=c("spp","assessmentyear"))
refs=transmute(refs,spp=spp,year=an(assessmentyear),ref=variable,data=an(value))
refs=merge(refs,data.frame(ref=unique(refs$ref),qname=c(rep("F",4),rep("SSB",3))))

load(file.path(dropboxdir, "data/om/whbRet.RData"))
load(file.path(dropboxdir, "data/om/herRet.RData"))
load(file.path(dropboxdir, "data/om/macRet.RData"))

load(file.path(dropboxdir, "data/om/whbErr.RData"))
load(file.path(dropboxdir, "data/om/herErr.RData"))
load(file.path(dropboxdir, "data/om/macErr.RData"))

```

# Hindcast analysis of pelagic stocks

## Blue whiting, North Sea herring and Northeast Atlantic mackerel

**L. Kell, M.A. Pastoors

`r format(Sys.time(), '%d/%m/%Y')`


# Introduction

Description of the issues

Approach

# Reference points

Historical estimates of reference points. MSY at SSB refers to MSY Btrigger. 

```{r refs, fig.asp=0.6, warning=FALSE}
refplots <- list()

refplots[["f"]] <-
  refs %>% 
  filter(ref %in% c("fpa", "fmsy", "flim")) %>%
  mutate(ref = gsub("f","", ref)) %>% 
  mutate(ref = factor(ref, levels=c("lim","pa", "msy"))) %>% 
  dplyr::rename(variable = qname) %>% 
  
  ggplot()+
  geom_line( aes(year,as.numeric(data),colour=ref))+
  geom_point(aes(year,as.numeric(data),colour=ref))+
  labs(x="", y="") +
  expand_limits(y=0) +
  facet_grid(spp~variable,scale="free")

refplots[["ssb"]] <-
  refs %>% 
  filter(ref %in% c("blim","bpa","msybtrigger")) %>% 
  mutate(ref = gsub("^b","", ref)) %>% 
  mutate(ref = gsub("btrigger","", ref)) %>% 
  mutate(ref = factor(ref, levels=c("lim","pa", "msy"))) %>% 
  dplyr::rename(variable = qname) %>% 
  
  ggplot()+
  geom_line( aes(year,as.numeric(data),colour=ref))+
  geom_point(aes(year,as.numeric(data),colour=ref))+
  labs(x="", y="") +
  expand_limits(y=0) +
  facet_grid(spp~variable,scale="free")

ggarrange(
  refplots[["ssb"]]+theme_bw()+
  theme(panel.grid.major =element_blank(),
        strip.background.y = element_blank(), strip.text.y = element_blank(),
        # axis.ticks       =element_blank(),
        # axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)),
          
  refplots[["f"]]+theme_bw()+
  theme(panel.grid.major =element_blank(),
        # axis.ticks       =element_blank(),
        # axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)), 
          
  nrow = 1,ncol=2,
  common.legend=TRUE, legend = "bottom")


```

**Figure `r iFig=iFig+1; iFig`** ICES SSB and Fishing Mortality reference points, as estimated at each benchmark assessment.

\newpage

# Assessment

Most recent assessments (2022) relative to historical estimates of reference points. 

```{r, assessment, warning=FALSE}

assessment =list()

assessment[["whb"]] <-
  ggplotFL::plot(window(whb, 1990))+  
  
  geom_line(data = filter(refs, 
                          spp=="Blue whiting" & 
                          ref %in%c("blim","bpa","msybtrigger", "fmsy", "fpa")),
            aes(year, data, col=ref)) +
  theme(legend.position="bottom")+
  scale_color_manual("Reference\nPoints",values=rainbow(7))

assessment[["her"]] <-
  plot(window(her, 1990))+  
  geom_line(data = filter(refs, 
                          spp=="Herring" & 
                          ref %in%c("blim","bpa","msybtrigger", "fmsy", "fpa")),
            aes(year, data, col=ref)) +
  #scale_color_manual(values=c("red","blue"))+
  theme(legend.position="bottom")+
  scale_color_manual("Reference\nPoints",values=rainbow(7))

assessment[["mac"]] <- 
  plot(window(mac, 1990))+  
  geom_line(data = filter(refs, 
                          spp=="Mackerel" & 
                          ref %in%c("blim","bpa","msybtrigger", "fmsy", "fpa")),
            aes(year, data, col=ref)) +
  #scale_color_manual(values=c("red","blue"))+
  theme(legend.position="bottom")+
  scale_color_manual("Reference\nPoints",values=rainbow(7))

# plot together

ggarrange(
  assessment[["whb"]]+theme_bw()+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)),
          
  assessment[["her"]]+theme_bw()+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)),
          
  assessment[["mac"]]+theme_bw()+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)), 
          nrow = 1,ncol=3,
          common.legend=TRUE, legend = "bottom",
          labels = c("WHB","HER","MAC"))
```

**Figure `r iFig=iFig+1; iFig`** Most recent ICES assessments with F and SSB reference points

\newpage

## Retrospective analyses

```{r, whb-retro, warning=FALSE, fig.asp=1.0}

retros=
  list(
    "whb"=plot(window(whbRet,start=1990),
               metrics=list("SSB"=ssb,"F"=fbar, "rec"=rec))+
            theme_bw()+ 
            theme(legend.position="none")
  )

# retros[["whb"]]

retros[["her"]]=
  plot(
    window(herRet,start=1990),
    metrics=list("SSB"=ssb,"F"=fbar, "rec"=rec)
  )+
  theme_bw()+ 
  theme(legend.position="none") 

# retros[["her"]]

retros[["mac"]]=plot(window(macRet,start=1990),metrics=list("SSB"=ssb,"F"=fbar, "rec"=rec))+
  theme_bw()+ 
  theme(legend.position="none")

# retros[["mac"]]+facet_grid(.~qname)

ggarrange(
  retros[["whb"]]+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA))+
  expand_limits(y=0),

  retros[["her"]]+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)) +
  expand_limits(y=0),
          
  retros[["mac"]]+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA))+
  expand_limits(y=0),
  
  nrow = 1,ncol=3,
  common.legend=TRUE, legend="none",
  labels = c("WHB","HER","MAC"), 
  label.x = rep(0.06,3),
  label.y = rep(0.99,3)) 

```

**Figure `r iFig=iFig+1; iFig`** Retrospective analysis for ICES assessments. 


## Assessment Error

```{r, whb-err, fig.height=8, fig.width=8, warning=FALSE}
# library(grid) 

# CAN WE CONDENSE INTO THREE FIGURES ON A PAGE??

dt=as.data.frame(rmvnorm(1000,c(1,1),cov(whbErr[-1,])))
names(dt)=c("stock","harvest")
kobePhaseMar(dt,quadcol=c("white","white","white","white"), xlab="F",ylab="SSB")

dt=as.data.frame(rmvnorm(1000,c(1,1),cov(herErr[-1,])))
names(dt)=c("stock","harvest")
kobePhaseMar(dt,quadcol=c("white","white","white","white"), xlab="F",ylab="SSB")

dt=as.data.frame(rmvnorm(1000,c(1,1),cov(macErr[-1,])))
names(dt)=c("stock","harvest")
kobePhaseMar(dt,quadcol=c("white","white","white","white"), xlab="F",ylab="SSB")

# ggarrange stuff here

```

**Figure `r iFig=iFig; iFig`c** Blue whiting, Herring and Mackerel: assessment error


\newpage

## Harvest control rules


\newpage

# Blue whiting

## Comparing ICES assessment, VPA reconstruction and forward prediction from VPA with observed catches

Note the difference in F and SSB between ICES assessment and VPA reconstruction. 

[ WHY IS THERE NO DIFFERENCE IN RECRUITMENT FOR BLUE WHITING ?? ]

```{r, whb-fmsy, warning=FALSE, fig.asp=1.0}
load(file.path(dropboxdir, "data/inputs/WHB/run/model.RData"))
load(file.path(dropboxdir, "data/om/whb.RData"))

vpa = whb + FLAssess:::VPA(whb)

whbFtar=as.FLQuant(subset(refs,spp=="Blue whiting"&ref=="fmsy"&year>=2001)[,c("year","data")])[,-22]
whbFtar[is.na(whbFtar)]=0.22

x=fit
sd=FLQuant(x[["sdrep"]][["diag.cov.random"]][names(x[["sdrep"]][[7]])=="logN"],dimnames=list(age=0:12,year=1980:2022))^0.5
stock.n(vpa)=rlnorm(nits,log(stock.n(whb)),sd[1:10,ac(1981:2022)])

whb    =propagate(whb,nits)
whbCtc =fwd(whb,catch=catch(whb)[,ac(2001:2021)],sr=rec(vpa))
whbFmsy=fwd(whb,f=whbFtar,                       sr=rec(vpa))

pwhb=plot(window(FLStocks("ICES"=whb,
                          "VPA"=vpa,
                          "VPA+Reported catch"=whbCtc),
          1990))+
   scale_x_continuous(breaks=c(2001,2011,2021))

pwhb$data$qname=factor(pwhb$data$qname,levels=c("Rec","F","Catch","SSB"))

# plot comparing the three scenarios
pwhb$data %>% 
  ggplot(aes(x=year, y=data, group=iter)) +
  theme_bw() +
  geom_line() +
  labs(title = "whb") +
  facet_grid(qname~stock, scales="free_y") 

# plot overlay
pwhb

```

## Projections based on ICES assessment

```{r, whbProj, warning=FALSE, fig.asp=1.0}
whbFtar=as.FLQuant(subset(refs,spp=="Blue whiting"&ref=="fmsy"&year>=2001)[,c("year","data")])[,-22]
whbFtar[is.na(whbFtar)]=0.18

# forward projection using historical Ftarget=Fmsy
whbFwd =prj(whb,whbFtar)

# forward projection using  most recent Fmsy
whbFwd2=prj(whb,whbFtar%=% c(whbFtar[,dim(whbFtar)[2]]))

proj=list(
  "whb"=plot(window(FLStocks("Fmsy"=whbFwd,
                             "Fmsy 2021"=whbFwd2,
                             "ICES"=whb),
                    start=1990,end=2020))+
  scale_colour_manual("Scenario",values=c("red","blue","black"))+
  theme_bw()+
  theme(legend.position="bottom"))

proj[["whb"]]

```





# North Sea herring

## Comparing ICES assessment, VPA reconstruction and forward prediction from VPA with observed catches

Note the difference in F and SSB between ICES assessment and VPA reconstruction. 

```{r, her-fmsy, warning=FALSE, fig.asp=1.0}
load(file.path(dropboxdir, "data/inputs/HER/NSAS_HAWG2022_sf_replicates.RData"))
load(file.path(dropboxdir, "data/om/her.RData"))

herFtar=as.FLQuant(subset(refs,spp=="Herring"&ref=="fmsy"&year>=2001)[,c("year","data")])[,-22]
herFtar[is.na(herFtar)]=0.25

res=melt(laply(NSH.sim,stock.n))
names(res)=c("iter","age","year","data")
recs=as.FLQuant(res)[1,,,,,1:nits]

vpa=her+FLAssess:::VPA(her)

her=propagate(her,nits)  
herCtc =fwd(her,catch=catch(her)[,ac(2001:2021)],sr=rec(vpa)%*%(recs%/%apply(recs,2,median))[,-76])
herFmsy=fwd(her,f=    herFtar, sr=rec(vpa)%*%(recs%/%apply(recs,2,median))[,-76])
pher=plot(window(FLStocks("ICES"=her,
                          "VPA"=vpa,
                          "VPA+Reported catch"=herCtc),
          1995))+
   scale_x_continuous(breaks=c(2001,2011,2021))

pher$data$qname=factor(pher$data$qname,levels=c("Rec","F","Catch","SSB"))

# plot comparing the three scenarios
pher$data %>% 
  ggplot(aes(x=year, y=data, group=iter)) +
  theme_bw() +
  geom_line() +
  labs(title = "her") +
  facet_grid(qname~stock, scales="free_y") 

pher

```
## Projections

```{r, herProj, warning=FALSE, fig.asp=1.0}

herFtar=as.FLQuant(subset(refs,spp=="Herring"&ref=="fmsy"&year>=2001)[,c("year","data")])[,-22]
herFtar[is.na(herFtar)]=0.25

herFwd=prj(her,herFtar)
herFwd2=prj(her,herFtar%=%c(herFtar[,dim(herFtar)[2]]))

proj[["her"]]=plot(window(FLStocks("Fmsy"=herFwd,
                                   "Fmsy 2021"=herFwd2,
                                   "ICES"=her),
                          start=1990,end=2020))+
  scale_colour_manual("Scenario",values=c("red","blue","black"))+
  theme_bw()+ 
  theme(legend.position="bottom")

proj[["her"]]

```






# Northeast Atlantic Mackerel

## Comparing ICES assessment, VPA reconstruction and forward prediction from VPA with observed catches

Note strong difference in recruitment between ICES assessment and VPA based assessments.

```{r, mac-fmsy, warning=FALSE, fig.asp=1.0}

load(file.path(dropboxdir, "data/inputs/MAC/model fit.RData"))
load(file.path(dropboxdir, "data/om/mac.RData"))

x=fit.new 
snVar=FLQuant(x[["sdrep"]][["diag.cov.random"]][names(x[["sdrep"]][[7]])=="logN"],dimnames=list(age=0:12,year=1980:2022))^0.5

vpa=mac+FLAssess:::VPA(mac)
stock.n(vpa)=rlnorm(nits,propagate(log(stock.n(vpa)),nits),snVar[,-43])

macFtar=as.FLQuant(subset(refs,spp=="Mackerel"&ref=="fmsy"&year>=2001)[,c("year","data")])[,-22]
macFtar[is.na(macFtar)]=0.22

#x=fit.new
#sd=FLQuant(x[["sdrep"]][["diag.cov.random"]][names(x[["sdrep"]][[7]])=="logN"],dimnames=list(age=0:12,year=1980:2022))^0.5
#stock.n(mac)=rlnorm(nits,log(stock.n(mac)),sd[,ac(1980:2021)])

macCtc =fwd(propagate(mac,nits),catch=catch(mac)[,ac(2001:2021)],sr=rec(vpa))
macFmsy=fwd(propagate(mac,nits),f=    macFtar,                   sr=rec(vpa))
pmac=plot(window(FLStocks("ICES"=mac,
                          "VPA"=vpa,
                          #"ICES-f"  =fwd(mac,f=    fbar( mac)[,ac(2001:2021)],sr=rec(vpa)),
                          #"Fmsy"    =macFmsy,
                          "VPA+Reported catch"=macCtc),
          1995))+
   # geom_line(aes(year,data,col=stock),
   #          data=transform(subset(refs,spp=="Mackerel"&ref%in%c("blim","bpa","msybtrigger")),stock=ref))+
   # scale_color_manual(values=c("red","blue","green","orange","pink","purple"))+
   scale_x_continuous(breaks=c(2001,2011,2021))

pmac$data$qname=factor(pmac$data$qname,levels=c("Rec","F","Catch","SSB"))

mac=fwd(propagate(mac,nits),catch=catch(mac)[,ac(2001:2021)],sr=rec(vpa))

# plot comparing the three scenarios
pmac$data %>% 
  ggplot(aes(x=year, y=data, group=iter)) +
  theme_bw() +
  geom_line() +
  labs(title = "mac") +
  facet_grid(qname~stock, scales="free_y") 

pmac

```

## Projections

```{r, macProj, warning=FALSE, fig.asp=1.0}

macFtar=as.FLQuant(subset(refs,spp=="Mackerel"&ref=="fmsy"&year>=2001)[,c("year","data")])[,-22]
macFtar[is.na(macFtar)]=0.22

macFwd=prj(mac,macFtar) 
macFwd2=prj(mac,macFtar%=%c(macFtar[,dim(macFtar)[2]]))
 
proj[["mac"]]=plot(window(FLStocks("Fmsy"=macFwd,
                                   "Fmsy 2021"=macFwd2,
                                   "ICES"=mac),
                          start=1990,end=2020))+
  scale_colour_manual("Scenario",values=c("red","blue","black"))+
  theme_bw()+
  theme(legend.position="bottom")

proj[["mac"]]

```








# Comparisons between stocks

## Comparing ICES assessment, VPA reconstruction and forward prediction from VPA with observed catches

```{r, hind, fig.asp=1.0, warning=FALSE}
library(ggpubr)
ggarrange(pwhb+theme_bw()+  
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)),
          pher+theme_bw()+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)),
          pmac+theme_bw()+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)), 
          nrow = 1,ncol=3,
          common.legend=TRUE, legend = "bottom",
          labels = c("WHB","HER","MAC")) 

```

**Figure `r iFig=iFig+1; iFig`** Comparison of ICES assessments with VPA, and projection from VPA with reported catches. 


## Projections

```{r, proj, fig.asp=1.0,warning=FALSE}
# library(ggpubr)  
ggarrange(proj[["whb"]]+theme_bw()+  
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)),
          proj[["her"]]+theme_bw()+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)),
          proj[["mac"]]+theme_bw()+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)), 
          nrow = 1,ncol=3,
          common.legend=TRUE, legend="bottom",
          labels = c("WHB","HER","MAC")) 

```

**Figure `r iFig=iFig+1; iFig`** Comparison of reported catch and $F_{MSY}$ projections at $F_{MSY}$. 


```{r}

whbRefs=FLQuants(dlply(subset(refs,spp=="Blue whiting"),.(ref), with, as.FLQuant(data.frame(year=year,data=data))))

herRefs=FLQuants(dlply(subset(refs,spp=="Herring"),     .(ref), with, as.FLQuant(data.frame(year=year,data=data))))

macRefs=FLQuants(dlply(subset(refs,spp=="Mackerel"),    .(ref), with, as.FLQuant(data.frame(year=year,data=data))))

# save(whb,whbFtar,whbErr,whbCtc,whbFmsy,whbRefs,file=file.path(dropboxdir,"data/om/whbOM.RData"))
# save(her,herFtar,herErr,herCtc,herFmsy,herRefs,file=file.path(dropboxdir,"data/om/herOM.RData"))
# save(mac,macFtar,macErr,macCtc,macFmsy,macRefs,file=file.path(dropboxdir,"data/om/macOM.RData")) 

```

**Figure `r iFig=iFig+1; iFig`** ICES Advice Rule.



```{r, eval=F}
load(file.path(dropboxdir, "data/inputs/MAC/model fit.RData"))
load(file.path(dropboxdir,"data/om/mac.RData"))

value=sam2FLQuant(fit.new)
sd   =sam2FLQuant(fit.new,2)

ggplot(mcf(FLQuants("FLStock"=catch(mac),"fit"=value[["catch"]])))+geom_line(aes(year,data,col=qname))

f   =FLQuant(exp(x[["pl"]][["logF"]]),dimnames=list(age=0:7,year=1980:2022),unit="f")
f   =FLCore:::expand(f,age=0:12)
f[ac(8:12)]=f[ac(7)]

sn=FLQuant(exp(x[[2]][["logN"]]),dimnames=list(age=0:12,year=1980:2022))
s2=FLQuant(x[["sdrep"]][[7]][names(x[["sdrep"]][[7]])=="logN"],dimnames=list(age=0:12,year=1980:2022))
x[["sdrep"]][["diag.cov.random"]]

snVar=FLQuant(x[["sdrep"]][["diag.cov.random"]][names(x[["sdrep"]][[7]])=="logN"],dimnames=list(age=0:12,year=1980:2022))^0.5

vpa=mac+FLAssess:::VPA(mac)

ftar=as.FLQuant(subset(refs,spp=="Mackerel"&ref=="fmsy"&year>=2001)[,c("year","data")])[,-22]
ftar[is.na(ftar)]=0.22

plot(window(FLStocks("ICES"=mac,"VPA"=vpa,"fwd"=fwd(vpa,f=fbar(mac)[,ac(2001:2021)],sr=rec(vpa)),
                     "ftar"=fwd(mac,f=ftar[,ac(2001:2021)],sr=rec(vpa)))))

res=fwd(mac,sr=rec(mac),control=control)


mac2=mac
harvest(mac2)=f[,ac(1980:2021)]
stock.n(mac2)=stkn[,ac(1980:2021)]

sn=x[[1]][[7]][names(x[[1]][[7]])=="logN"]
```

```{r, runWhb, cache=FALSE}

# Running or loading MSE results and making summary

stk="whb"
# source("../run/runHcr.R") 
load(file=paste(file.path(dropboxdir,paste("data/runs/",stk,".RData",sep=""))))

whb  = plot(window(FLStocks(llply(sims,function(x) x[[1]]))[c(1:6,9)],start=2001))
whbY = ldply(sims, function(x) as.data.frame(pmYear(window(x[[1]], start=2001)),drop=T))
whbI = ldply(sims, function(x) model.frame(pmIter(window(x[[1]], start=2001) )))

# whbI %>% filter(iter %in% 74:76) %>% View()

whbC=plot(FLQuants(llply(sims[-1],function(x) catch(window(x[[1]],start=2000,end=2021)))))+
  geom_line(aes(year,data),data=as.data.frame(apply(catch(sims[[1]][[1]]),2,median)[,ac(2000:2021)]),linetype=2)+
  facet_wrap(~qname)


whbS=plot(FLQuants(llply(sims[-1],function(x) ssb(window(x[[1]],start=2000,end=2021)))))+
  geom_line(aes(year,data),data=as.data.frame(apply(ssb(sims[[1]][[1]]),2,median)[,ac(2000:2021)]),linetype=2)+
  geom_line(aes(year,data),data=as.data.frame(refs$blim),col="red")+
  geom_line(aes(year,data),data=as.data.frame(refs$msybtrigger),col="blue")+
  # facet_grid(qname~.)
  facet_wrap(~qname)

whbF=plot(FLQuants(llply(sims[-1],function(x) fbar(window(x[[1]],start=2000,end=2021)))))+
  geom_line(aes(year,data),data=as.data.frame(apply(fbar(sims[[1]][[1]]),2,median)[,ac(2000:2021)]),linetype=2)+
  geom_line(aes(year,data),data=as.data.frame(refs$fmsy),col="blue")+
  # facet_grid(qname~.)
  facet_wrap(~qname)

# save(whbY,whbI,whbC,whbS,whbF,
#     file=file.path(dropboxdir,paste("data/results/",stk, "smry",".RData",sep="")))

# catch
p1 <-
  plot(
  FLQuants(llply(sims[c("HCR1", "HCR1 bnd","HCR1 +10% bnd", "HCR1 +20% bnd", "HCR1 +30% bnd")],
                 function(x) catch(window(x[[1]],start=2000,end=2021))) ))+
  geom_line(aes(year,data),
            data=as.data.frame(apply(catch(sims[[1]][[1]]),2,median)[,ac(2000:2021)]),
            linetype=2, col="blue", size=1)+
  expand_limits(y=0)  + 
  facet_grid(qname~.) # facet_wrap(~qname, ncol=1)

p1b <-
  filter(whbY, qname=="cCum", 
       .id %in% c("HCR1", "HCR1 bnd","HCR1 +10% bnd", "HCR1 +20% bnd", "HCR1 +30% bnd"), 
       year %in% 2000:2021) %>% 
  ggplot(aes(x=year, y=median, group=.id)) +
  geom_line(linewidth=1, colour="red") +
  geom_ribbon(aes(xmin=year, xmax=year, ymin=lowq, ymax=uppq), alpha=0.2, fill="red") +
  geom_line(data= filter(whbY, qname=="cCum", 
                               .id %in% c("ICES"), 
                               year %in% 2000:2021) %>% dplyr::select(-.id),
            aes(year,median), 
            col="blue", linewidth=1, linetype=2, inherit.aes=FALSE) +
  labs(y="") +
  expand_limits(y=0) +
  facet_grid(.id~.) # facet_wrap(~qname, ncol=1)


# ssb
p2 <-
  plot(
  FLQuants(llply(sims[c("HCR1", "HCR1 bnd","HCR1 +10% bnd", "HCR1 +20% bnd", "HCR1 +30% bnd")],
                 function(x) ssb(window(x[[1]],start=2000,end=2021)))))+
  geom_line(aes(year,data),
            data=as.data.frame(apply(ssb(sims[[1]][[1]]),2,median)[,ac(2000:2021)]),
            linetype=2, col="blue", size=1)+
  geom_line(aes(year,data),data=as.data.frame(refs$blim),col="red", size=1)+
  geom_line(aes(year,data),data=as.data.frame(refs$msybtrigger),col="blue", size=1) +
  facet_grid(qname~.) # facet_wrap(~qname, ncol=1)

# f
p3 <-
  plot(
  FLQuants(llply(sims[c("HCR1", "HCR1 bnd","HCR1 +10% bnd", "HCR1 +20% bnd", "HCR1 +30% bnd")],
                 function(x) fbar(window(x[[1]],start=2000,end=2021)))))+
  geom_line(aes(year,data),
            data=as.data.frame(apply(fbar(sims[[1]][[1]]),2,median)[,ac(2000:2021)]),
            linetype=2, col="blue", size=1)+
  geom_line(aes(year,data),data=as.data.frame(refs$fmsy),col="blue", size=1) +
  facet_grid(qname~.) # facet_wrap(~qname, ncol=1)


ggarrange(
  p1 +
  theme_bw()+
  theme(panel.grid.major =element_blank(),  
        strip.background.y = element_blank(), strip.text.y = element_blank(),
        # axis.ticks       =element_blank(),
        # axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)),
          
  p1b +
  theme_bw()+
  theme(panel.grid.major =element_blank(),  
        strip.background.y = element_blank(), strip.text.y = element_blank(),
        # axis.ticks       =element_blank(),
        # axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)),
  
  p2+theme_bw()+ 
  theme(panel.grid.major =element_blank(),
        strip.background.y = element_blank(), strip.text.y = element_blank(),
        # axis.ticks       =element_blank(),
        # axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)),

  p3+theme_bw()+ 
  theme(panel.grid.major =element_blank(),
        # axis.ticks       =element_blank(),
        # axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)),
  
  nrow = 1,ncol=4,
  common.legend=TRUE,
  labels = c("Catch", "Cum. Catch","SSB", "F"),
  label.x = rep(0.12,4),
  label.y = rep(0.98,4)) 



```

```{r, runHer, cache=FALSE}

stk="her" 
# source("../run/runHcr.R") 
load(file=paste(file.path(dropboxdir,paste("data/runs/",stk,".RData",sep=""))))

her=plot(window(FLStocks(llply(sims,function(x) x[[1]]))[c(1:6,9)],start=1991))
herY=ldply(sims, function(x) as.data.frame(pmYear(x[[1]]),drop=T))
herI=ldply(sims, function(x) model.frame(pmIter(x[[1]])))
herC=plot(FLQuants(llply(sims[-1],function(x) catch(window(x[[1]],start=2000,end=2021)))))+
  geom_line(aes(year,data),data=as.data.frame(catch(sims[[1]][[1]])[,ac(2000:2021)]),col="red")+facet_grid(qname~.)
herS=plot(FLQuants(llply(sims[-1],function(x) ssb(window(x[[1]],start=2000,end=2021)))))+
  geom_line(aes(year,data),data=as.data.frame(apply(ssb(sims[[1]][[1]]),2,median)[,ac(2000:2021)]),linetype=2)+
  geom_line(aes(year,data),data=as.data.frame(refs$blim),col="red")+
  geom_line(aes(year,data),data=as.data.frame(refs$bpa), col="orange")+
  geom_line(aes(year,data),data=as.data.frame(refs$msybtrigger),col="blue")+
  facet_grid(qname~.)
herF=plot(FLQuants(llply(sims[-1],function(x) fbar(window(x[[1]],start=2000,end=2021)))))+
  geom_line(aes(year,data),data=as.data.frame(apply(fbar(sims[[1]][[1]]),2,median)[,ac(2000:2021)]),linetype=2)+
  geom_line(aes(year,data),data=as.data.frame(refs$fmsy),col="blue")+
  facet_grid(qname~.)
  facet_wrap(~qname)

# save(herY,herI,herC,herS,herF,
#     file=file.path(dropboxdir,paste("data/results/",stk, "smry",".RData",sep="")))

```

```{r, runMac, cache=FALSE}

stk="mac"
# source("../run/runHcr.R") 
load(file=paste(file.path(dropboxdir,paste("data/runs/",stk,".RData",sep=""))))

load(file.path(dropboxdir,paste("data/runs/","mac",".RData",sep="")))
mac=plot(window(FLStocks(llply(sims,function(x) x[[1]]))[c(1:6,9)],start=1991))
macY=ldply(sims, function(x) as.data.frame(pmYear(x[[1]]),drop=T))
macI=ldply(sims, function(x) model.frame(pmIter(x[[1]]))) 
macC=plot(FLQuants(llply(sims[-1],function(x) catch(window(x[[1]],start=2000,end=2021)))))+
  geom_line(aes(year,data),data=as.data.frame(catch(sims[[1]][[1]])[,ac(2000:2021)]),col="red")+facet_grid(qname~.)
macS=plot(FLQuants(llply(sims[-1],function(x) ssb(window(x[[1]],start=2000,end=2021)))))+
  geom_line(aes(year,data),data=as.data.frame(apply(ssb(sims[[1]][[1]]),2,median)[,ac(2000:2021)]),linetype=2)+
  geom_line(aes(year,data),data=as.data.frame(refs$blim),col="red")+
  geom_line(aes(year,data),data=as.data.frame(refs$bpa), col="orange")+
  geom_line(aes(year,data),data=as.data.frame(refs$msybtrigger),col="blue")+
  facet_grid(qname~.)

# save(whbY,whbI,herY,herI,macY,macI,file=file.path(dropboxdir,paste("data/results/",stk, "smry",".RData",sep="")))


```

```{r, smry, cache=FALSE}





plot(
  FLQuants(llply(sims[c(2,3,4)],function(x) catch(window(x[[1]],start=2000,end=2021)))))+
  geom_line(data=as.data.frame(catch(sims[[1]][[1]])[,ac(2000:2021)]),
            aes(year,data), 
            col="blue", size=1) +
  expand_limits(y=0) 

plot(
  FLQuants(llply(sims[c("HCR1","HCR1 +10%", "HCR1 +20%", "HCR1 +30%")],
                 function(x) catch(window(x[[1]],start=2000,end=2021)))))+
  geom_line(data=as.data.frame(catch(sims[[1]][[1]])[,ac(2000:2021)]),
            aes(year,data), 
            col="blue", size=1) +
  expand_limits(y=0) 

plot(
  FLQuants(llply(sims[c("HCR1","HCR1 +10%", "HCR1 +20%", "HCR1 +30%")],
                 function(x) catch(window(x[[1]],start=2000,end=2021)))))+
  geom_line(data=as.data.frame(catch(sims[[1]][[1]])[,ac(2000:2021)]),
            aes(year,data), 
            col="blue", size=1) +
  expand_limits(y=0) 


```


```{r, smry-yr, fig.width=12,fig.height=6, cache=FALSE}
ggarrange(whb+theme_bw()+
  theme(panel.grid.major =element_blank(),  
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)),
          her+theme_bw()+ 
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)),
          mac+theme_bw()+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)), 
          nrow = 1,ncol=3,
          common.legend=TRUE,
          labels = c("WHB","HER","MAC"))
```

**Figure `r iFig=iFig+1; iFig`** MSEs

```{r, catch, fig.width=12,fig.height=8, cache=FALSE}
ggarrange(whbC+theme_bw()+ 
  theme(panel.grid.major =element_blank(),  
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)),
          herC+theme_bw()+ 
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)),
          macC+theme_bw()+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)), 
          nrow = 1,ncol=3,
          common.legend=TRUE,
          labels = c("WHB","HER","MAC"))
```

**Figure `r iFig=iFig+1; iFig`** Catches


```{r, ssb, fig.width=12,fig.height=8, cache=FALSE}
ggarrange(whbS+theme_bw()+ 
  theme(panel.grid.major =element_blank(),  
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)),
          herS+theme_bw()+ 
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)),
          macS+theme_bw()+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)), 
          nrow = 1,ncol=3,
          common.legend=TRUE,
          labels = c("WHB","HER","MAC"))
```

**Figure `r iFig=iFig+1; iFig`** SSB

```{r, smry-I, fig.width=12,fig.height=6, cache=FALSE}
load(file.path(dropboxdir,paste("data/results/","smry",".RData",sep=""))) 

p1=ggboxplot(subset(whbY,!.id%in%c("bbb")&qname!="rec"),y="median")+facet_grid(qname~.id,scale="free")
p2=ggboxplot(subset(herY,!.id%in%c("bbb")&qname!="rec"),y="median")+facet_grid(qname~.id,scale="free")
p3=ggboxplot(subset(macY,!.id%in%c("bbb")&qname!="rec"),y="median")+facet_grid(qname~.id,scale="free")

ggarrange(p1+theme_bw()+   
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)),
          p2+theme_bw()+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)),
          p3+theme_bw()+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)), 
          nrow = 1,ncol=3,
          common.legend=TRUE,
          labels = c("WHB","HER","MAC"))
```

```{r, fig.width=12,fig.height=6, cache=FALSE}
library(reshape)

calc_boxplot_stat <- function(x) {
  coef <- 1.5
  n <- sum(!is.na(x))
  # calculate quantiles
  stats <- quantile(x, probs = c(0.0, 0.25, 0.5, 0.75, 1.0))
  names(stats) <- c("ymin", "lower", "middle", "upper", "ymax")
  iqr <- diff(stats[c(2, 4)])
  # set whiskers
  outliers <- x < (stats[2] - coef * iqr) | x > (stats[4] + coef * iqr)
  if (any(outliers)) {
    stats[c(1, 5)] <- range(c(stats[2:4], x[!outliers]), na.rm = TRUE)
  }
  return(stats)
}


t <-
  whbI %>% 
  mutate(
    hcr = stringr::word(.id, 1, sep=" "),
    hcr = gsub("ICES","_ICES", hcr),
    
    cap = ifelse(grepl("cap", .id), "cap", ""),
    bnd = ifelse(grepl("bnd", .id), "bnd", ""),
    
    # .id = gsub(" bnd| cap","", .id), 
    # .id = gsub("1$","1 0%", .id), 
    # .id = gsub("2$","2 0%", .id), 
    
    impl = stringr::str_extract( .id, "[:digit:]{2}"),
    impl = ifelse(is.na(impl), "0", impl)
  ) %>% 
    dplyr::select(-iter) %>% 
  tidyr::pivot_longer(names_to="variable", values_to="data", catch.50:aav) %>% 
  dplyr::mutate(variable = factor(variable, levels=c("catch.50", "iav.50", "aav"))) 


# t %>% filter(grepl("%", .id)) %>% View()
# glimpse(t)

t %>% 
  # dplyr::select(-iter) %>% 
  # tidyr::pivot_longer(names_to="variable", values_to="data", catch.50:aav) %>% 
  # dplyr::mutate(variable = factor(variable, levels=c("catch.50", "iav.50", "aav"))) %>% 
  ggplot(aes(x=.id, y=data)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_boxplot() +
  facet_grid(variable~hcr+impl+bnd+cap, scales="free")

ggplot(diamonds, aes(x=cut, y=price, fill=cut)) + 
    stat_summary(fun.data = calc_boxplot_stat, geom="boxplot") + 
    facet_wrap(~clarity, scales="free")


t %>% 
  
  ggplot(aes(x=.id, y=data)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  stat_summary(fun.data = calc_boxplot_stat, geom="boxplot", aes(colour=hcr)) +
  # geom_boxplot(aes(colour=hcr), outlier.shape = NA) +
  expand_limits(y=0) +
  # scale_y_continuous(limits = quantile(t$data, c(0.1, 0.9))) +
  facet_grid(variable~impl+bnd+cap, scales="free", space="free_x")
  



p1=ggboxplot(melt(whbI[,-5],id=".id"),y="value")+facet_grid(variable~.id,scale="free")
p2=ggboxplot(melt(herI[,-5],id=".id"),y="value")+facet_grid(variable~.id,scale="free")
p3=ggboxplot(melt(macI[,-5],id=".id"),y="value")+facet_grid(variable~.id,scale="free")
 
ggarrange(p1+theme_bw()+   
  theme(panel.grid.major =element_blank(), 
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)),
          p2+theme_bw()+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)),
          p3+theme_bw()+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)), 
          nrow = 1,ncol=3,
          common.legend=TRUE,
          labels = c("WHB","HER","MAC"))
```



```{r, cache=FALSE}
load(file.path(dropboxdir,paste("data/results/","smry",".RData",sep=""))) 

lvls=c("ICES","Fmsy",
       "HCR1",
       "HCR1 +10%","HCR1 +20%","HCR1 +30%",
       "HCR1 bnd","HCR1 +10% bnd","HCR1 +20% bnd","HCR1 +30% bnd",
       "HCR1 bnd cap","HCR1 +10% bnd cap","HCR1 +20% bnd cap","HCR1 +30% bnd cap",
       "HCR2",
       "HCR2 +10%","HCR2 +20%","HCR2 +30%",
       "HCR2 bnd","HCR2 +10% bnd","HCR2 +20% bnd","HCR2 +30% bnd",
       "HCR2 bnd cap","HCR2 +10% bnd cap","HCR2 +20% bnd cap","HCR2 +30% bnd cap")
                                     
whbY=transform(whbY,.id=factor(.id,levels=lvls))
cast(subset(transform(whbY,median=round(median/1000),0),qname=="catch"&year>2000&year<2022),.id~year,value="median")
```


```{r, cache=FALSE}
herY=transform(herY,.id=factor(.id,levels=lvls))  
cast(subset(transform(herY,median=round(median/1000),0),qname=="catch"&year>2000&year<2022),.id~year,value="median")
```


```{r, cache=FALSE}
macY=transform(macY,.id=factor(.id,levels=lvls))
cast(subset(transform(macY,median=round(median/1000),0),qname=="catch"&year>2000&year<2022),.id~year,value="median")
```

# Funding

# References
