---
title: "**Pelagics**"
subtitle: "Operating Model Conditioning"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
mathjax: TRUE
fig_width: 6 
fig_height: 4 
tags: FLR FLCore introduction
license: Creative Commons Attribution-ShareAlike 4.0 International Public License
# bibliography: refs.bib
---


```{r, knitr, eval=TRUE, echo=FALSE, warning=FALSE, cache=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# getwd()
library(knitr)

opts_chunk$set(cache     =TRUE, 
               comment   =NA, 
               warning   =FALSE, 
               message   =FALSE, 
               error     =FALSE, 
               echo      =FALSE, 
               eval      =TRUE,cache   =TRUE,
               cache.path="../cache/figs/cond/",
               fig.path  ="../tex/figs",
               fig.width =8,
               fig.height=6,
               dev       ="png")

iFig=1
iTab=0
```

```{r}
nits=100
```

```{r, pkgs}
#install_github("flr/FLfse/FLfse")
#install.packages("FLBRP", repos="http://flr-project.org/R")
#remotes::install_github("flr/FLasher")
#remotes::install_github('fishfollower/SAM/stockassessment', ref='components')
#remotes::install_github("flr/FLSAM")
  
library(FLCore) 
library(ggplotFL)
library(FLfse)
library(FLBRP)
library(FLasher)
library(FLSAM)
library(kobe)   #remotes::install_github("flr/kobe")

library(rjson) # install.packages("rjson"); used for dropbox function
library(RJSONIO)

library(TMB)
library(stockassessment)
  
library(plyr)
library(dplyr)
library(reshape)
library(magrittr)
  
library(grid) 
library(ggpubr)

library(compositions)

theme_set(theme_bw(16))
```

```{r, source}
source('../R/kobe-phaseMar.R')
source('../R/kobe-phase.R')
source('../R/get_dropbox.r')
```


```{r, dbox}
dropboxdir<-try(file.path(get_dropbox(), "pelagics"))

if ("try-error"%in%is(dropboxdir))
  dropboxdir="~/Dropbox/pelagics"
```


```{r, source2}
prj<-function(x,ftar,
              yrs=dimnames(x)$year[dim(m(x))[2]-31:0],nit=nits){
  f0=array(c(rep(c(1,rep(0,dim(x)[1])),dim(x)[1]-1),1),c(dim(harvest(x))[1],dim(harvest(x))[1]),
           dimnames=list(dims(x)$min:dims(x)$max,dims(x)$min:dims(x)$max))
  f0=f0*0.05
  F0=aperm(maply(data.frame(year=yrs), function(year) rlnorm.rplus(nits,rep(0,dim(x)[1]),f0)),c(3,1,2)) 
  names(dimnames(F0))[c(1,3)]=c("age","iter")
  F0=as.FLQuant(c(F0),dimnames=dimnames(F0))
  
  x=propagate(x,nit)
  stock.n(x)[,ac(yrs)]=stock.n(x)[,ac(yrs)]%*%F0
  
  control=as(FLQuants("f"=ftar),"fwdControl")
  
  res=fwd(x,sr=rec(x),control=control)
  res}

load(file.path(dropboxdir, "data/inputs/MAC/model fit.RData"))

sam2FLQuant<-function(x,row=1){
  FLQuants(ssb     =FLQuant(x[["sdrep"]][[row]][names(x[["sdrep"]][["value"]])=="logssb"],   dimnames=list(year=x[["data"]][["years"]])),
           fbar    =FLQuant(x[["sdrep"]][[row]][names(x[["sdrep"]][["value"]])=="logfbar"],  dimnames=list(year=x[["data"]][["years"]])),
           catch   =FLQuant(x[["sdrep"]][[row]][names(x[["sdrep"]][["value"]])=="logCatch"], dimnames=list(year=x[["data"]][["years"]])),
           landings=FLQuant(x[["sdrep"]][[row]][names(x[["sdrep"]][["value"]])=="logLand"],  dimnames=list(year=x[["data"]][["years"]])),
           rec     =FLQuant(x[["sdrep"]][[row]][names(x[["sdrep"]][["value"]])=="logR"],     dimnames=list(year=x[["data"]][["years"]])),
           biomass =FLQuant(x[["sdrep"]][[row]][names(x[["sdrep"]][["value"]])=="logtsb"],   dimnames=list(year=x[["data"]][["years"]])))}
```

```{r, assessment-whb}
load(file.path(dropboxdir, "data/inputs/WHB/run/model.RData"))

whb=SAM2FLStock(fit)
whbR=FLBRP(whb,nyears=20)
params(whbR)[]=median(rec(whb))

catch(whb)=computeCatch(whb,"all")

save(whb,whbR,file=file.path(dropboxdir, "data/om/whb.RData"))
```

```{r, assessment-her}
load(file.path(dropboxdir, "data/inputs/HER/NSAS_HAWG2022_sf.RData"))

her=NSH
herR=FLBRP(her,nyears=20)
params(herR)[]=median(rec(her))

catch(her)=computeCatch(her,"all")

save(her,herR,file=file.path(dropboxdir, "data/om/her.RData"))
```

```{r, assessment-mac}
load(file.path(dropboxdir, "data/inputs/MAC/model fit.RData"))

mac =SAM2FLStock(fit.new)
mac=window(mac,end=2021)
macR=FLBRP(mac,nyears=20)
params(macR)[]=median(rec(mac))

catch(mac)=computeCatch(mac,"all")

save(mac,macR,file=file.path(dropboxdir, "data/om/mac.RData"))
```

```{r, retro-whb}
load(file.path(dropboxdir, "data/inputs/WHB/run/retro.RData"))

whbRet=FLStocks(llply(RETRO, SAM2FLStock)) 

save(whbRet,file=file.path(dropboxdir, "data/om/whbRet.RData"))
```

```{r, retro-her}
load(file.path(dropboxdir, "data/inputs/HER/NSAS_HAWG2022_sf_retro.RData"))
load(file.path(dropboxdir, "data/om/her.RData"))

herRet=FLStocks(llply(NSH.retro, function(x) {
  res         =window(her,end=dims(x)$maxyear)
  stock.n(res)=stock.n(x)
  harvest(res)=harvest(x)
  res}))

save(herRet,file=file.path(dropboxdir, "data/om/herRet.RData"))
```

```{r, retro-mac}
load(file.path(dropboxdir, "data/inputs/MAC/retro.RData"))
macRet=FLStocks(llply(ret,SAM2FLStock))

save(macRet,file=file.path(dropboxdir, "data/om/macRet.RData"))
```


```{r, whbErr}
load(file.path(dropboxdir, "data/om/whbRet.RData"))

om1=whbRet[[1]]
whbErr=laply(whbRet, function(x){
  yr=ac(dims(fbar(x))$maxyear)
  
  c(f  =c(fbar(x)[,yr]/fbar(om1)[,yr]),
    ssb=c(ssb(x)[,yr])/c(ssb(om1)[,yr]))})

save(whbErr,file=file.path(dropboxdir, "data/om/whbErr.RData"))
```

```{r, herErr}
# load("../data/inputs/HER/NSAS_HAWG2022_sf.RData")
load(file.path(dropboxdir, "data/om/herRet.RData"))

om1=herRet[[1]]
herErr=laply(herRet, function(x){
  yr=ac(dims(fbar(x))$maxyear)
  
  c(f  =c(fbar(x)[,yr]/fbar(om1)[,yr]),
    ssb=c(ssb(x)[,yr])/c(ssb(om1)[,yr]))})

save(herErr,file=file.path(dropboxdir, "data/om/herErr.RData"))
# save(herErr, file="../data/om/herErr.RData")
```

```{r, macErr}
load(file.path(dropboxdir, "data/om/macRet.RData"))
# load("../data/om/macRet.RData")

om1=macRet[[1]]
macErr=laply(macRet, function(x){
  yr=ac(dims(fbar(x))$maxyear)
  
  c(f  =c(fbar(x)[,yr]/fbar(om1)[,yr]),
    ssb=c(ssb(x)[,yr])/c(ssb(om1)[,yr]))})

save(macErr,file=file.path(dropboxdir, "data/om/macErr.RData"))
# save(macErr, file="../data/om/macErr.RData")
```

```{r, data}
load(file.path(dropboxdir,"data/om/whb.RData"))
load(file.path(dropboxdir,"data/om/her.RData"))
load(file.path(dropboxdir,"data/om/mac.RData")) 

refs=read.csv(file.path(dropboxdir,"data/inputs/refs.csv"),header=T)
refs=melt(refs,measure=c("flim","fpa","fmsy","fcap","blim","bpa","msybtrigger"),id=c("spp","assessmentyear"))
refs=transmute(refs,spp=spp,year=an(assessmentyear),ref=variable,data=an(value))
refs=merge(refs,data.frame(ref=unique(refs$ref),qname=c(rep("F",4),rep("SSB",3))))

load(file.path(dropboxdir, "data/om/whbRet.RData"))
load(file.path(dropboxdir, "data/om/herRet.RData"))
load(file.path(dropboxdir, "data/om/macRet.RData"))

load(file.path(dropboxdir, "data/om/whbErr.RData"))
load(file.path(dropboxdir, "data/om/herErr.RData"))
load(file.path(dropboxdir, "data/om/macErr.RData"))
```


```{r, whb}
assessment=list(whb=plot(whb)+  
  geom_line(aes(year,data,col=stock),
            data=transform(subset(refs,spp=="Blue whiting"&ref%in%c("blim","bpa","msybtrigger")),stock=ref))+
  #scale_color_manual(values=c("red","blue"))+
  theme(legend.position="bottom")+
  scale_color_manual("Reference\nPoints",values=rainbow(7)))
```


```{r, her}
assessment[["her"]]=plot(her)+  
  geom_line(aes(year,data,col=stock),
            data=transform(subset(refs,spp=="Herring"&ref%in%c("blim","bpa","msybtrigger")),stock=ref))+
  #scale_color_manual(values=c("red","blue"))+
  theme(legend.position="bottom")+
  scale_color_manual("Reference\nPoints",values=rainbow(7))
```


```{r, mac}
assessment[["mac"]]=plot(mac)+  
  geom_line(aes(year,data,col=stock),
            data=transform(subset(refs,spp=="Mackerel"&ref%in%c("blim","bpa","msybtrigger")),stock=ref))+
  #scale_color_manual(values=c("red","blue"))+
  theme(legend.position="bottom")+
  scale_color_manual("Reference\nPoints",values=rainbow(7))
```


```{r, assessment, fig.width=12,fig.height=6, cache=FALSE}
library(ggpubr)
ggarrange(assessment[["whb"]]+theme_bw()+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)),
          assessment[["her"]]+theme_bw()+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)),
          assessment[["mac"]]+theme_bw()+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)), 
          nrow = 1,ncol=3,
          common.legend=TRUE,
          labels = c("WHB","HER","MAC"))
```

**Figure `r iFig=iFig+1; iFig`** Most recent ICES assessments


```{r, frefs, fig.width=10,fig.height=6}
ref2=read.csv(file.path(dropboxdir,"data/inputs/refs.csv"),header=T)

fref=ggplot(melt(ref2[,c("spp","assessmentyear","flim","fpa","fmsy")],id.vars=c("spp","assessmentyear")))+
  geom_line( aes(assessmentyear,as.numeric(value),colour=variable))+
  geom_point(aes(assessmentyear,as.numeric(value),colour=variable))+
  facet_grid(spp~.,scale="free")+
  xlab("Year")+ylab("F")

fref
```

**Figure `r iFig=iFig+1; iFig`a** ICES Fishing Mortality reference points, as estimated at each benchmark assessment.

```{r, brefs, fig.width=10,fig.height=6}
bref=ggplot(melt(ref2[,c("spp","assessmentyear","blim","bpa","msybtrigger")],id.vars=c("spp","assessmentyear")))+
  geom_line( aes(assessmentyear,as.numeric(value)/1000,colour=variable))+
  geom_point(aes(assessmentyear,as.numeric(value)/1000,colour=variable))+
  facet_grid(spp~.,scale="free")+
  xlab("Year")+ylab("SSB (tn)")

bref
```

**Figure `r iFig=iFig; iFig`b** ICES Spawning Stock Biomass reference points, as estimated at each benchmark assessment.

```{r, refs, fig.width=12,fig.height=6}
p=ggarrange(fref+theme_bw()+ 
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)),
          bref+theme_bw()+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)), 
          nrow = 1,ncol=2,
          common.legend=TRUE)
```


```{r,eval=FALSE}
geom_polygon(aes(x,y,fill=f),data=quad,alpha=0.2)+
  geom_vline(aes(xintercept=x),data=data.frame(y="2FMSY",x=c( 90,105)),col="red")+
  geom_vline(aes(xintercept=x),data=data.frame(y="2FMSY",x=c( 80,110)),col="orange")+
  scale_fill_manual(values=c("orange","orange","green","green","red","blue"))
```


```{r, whb-fmsy}
load(file.path(dropboxdir, "data/inputs/WHB/run/model.RData"))

vpa=whb+FLAssess:::VPA(whb)

whbFtar=as.FLQuant(subset(refs,spp=="Blue whiting"&ref=="fmsy"&year>=2001)[,c("year","data")])[,-22]
whbFtar[is.na(whbFtar)]=0.22

x=fit
sd=FLQuant(x[["sdrep"]][["diag.cov.random"]][names(x[["sdrep"]][[7]])=="logN"],dimnames=list(age=0:12,year=1980:2022))^0.5
stock.n(vpa)=rlnorm(nits,log(stock.n(whb)),sd[1:10,ac(1981:2022)])

whb    =propagate(whb,nits)
whbCtc =fwd(whb,catch=catch(whb)[,ac(2001:2021)],sr=rec(vpa))
whbFmsy=fwd(whb,f=    whbFtar,                   sr=rec(vpa))
pwhb=plot(window(FLStocks("Original"=whb,
                          #"ICES-f"  =fwd(whb,f=    fbar( whb)[,ac(2001:2021)],sr=rec(vpa)),
                          "ICES-ctc"=whbCtc,
                          "Fmsy"    =whbFmsy),
          1995))+
   geom_line(aes(year,data,col=stock),
            data=transform(subset(refs,spp=="Blue whiting"&ref%in%c("blim","bpa","msybtrigger")),stock=ref))+
   scale_color_manual(values=c("red","blue","green","orange","pink","purple"))+
   scale_x_continuous(breaks=c(2001,2011,2021))

pwhb$data$qname=factor(pwhb$data$qname,levels=c("Rec","F","Catch","SSB"))
```

```{r, her-fmsy}
herFtar=as.FLQuant(subset(refs,spp=="Herring"&ref=="fmsy"&year>=2001)[,c("year","data")])[,-22]
herFtar[is.na(herFtar)]=0.25

load(file.path(dropboxdir, "data/inputs/HER/NSAS_HAWG2022_sf_replicates.RData"))
res=melt(laply(NSH.sim,stock.n))
names(res)=c("iter","age","year","data")
recs=as.FLQuant(res)[1,,,,,1:nits]

vpa=her+FLAssess:::VPA(her)

her=propagate(her,nits)  
herCtc =fwd(her,catch=catch(her)[,ac(2001:2021)],sr=rec(vpa)%*%(recs%/%apply(recs,2,median))[,-76])
herFmsy=fwd(her,f=    herFtar, sr=rec(vpa)%*%(recs%/%apply(recs,2,median))[,-76])
pher=plot(window(FLStocks("VPA"=vpa,
                          "Original"=her,
                          #"ICES-f"  =fwd(her,f=    fbar( her)[,ac(2001:2021)],sr=recs),
                          "ICES-ctc"=herCtc,
                          "Fmsy"    =herFmsy)[2:4],
          1995))+
   geom_line(aes(year,data,col=stock),
             data=transform(subset(refs,spp=="Herring"&ref%in%c("blim","bpa","msybtrigger")),stock=ref))+
   scale_color_manual(values=c("red","blue","green","orange","pink","purple","grey"))+
   scale_x_continuous(breaks=c(2001,2011,2021))

pher$data$qname=factor(pher$data$qname,levels=c("Rec","F","Catch","SSB"))
```

```{r, mac-fmsy}
load(file.path(dropboxdir, "data/inputs/MAC/model fit.RData"))

x=fit.new 
snVar=FLQuant(x[["sdrep"]][["diag.cov.random"]][names(x[["sdrep"]][[7]])=="logN"],dimnames=list(age=0:12,year=1980:2022))^0.5

vpa=mac+FLAssess:::VPA(mac)
stock.n(vpa)=rlnorm(nits,propagate(log(stock.n(vpa)),nits),snVar[,-43])

macFtar=as.FLQuant(subset(refs,spp=="Mackerel"&ref=="fmsy"&year>=2001)[,c("year","data")])[,-22]
macFtar[is.na(macFtar)]=0.22

#x=fit.new
#sd=FLQuant(x[["sdrep"]][["diag.cov.random"]][names(x[["sdrep"]][[7]])=="logN"],dimnames=list(age=0:12,year=1980:2022))^0.5
#stock.n(mac)=rlnorm(nits,log(stock.n(mac)),sd[,ac(1980:2021)])

macCtc =fwd(propagate(mac,nits),catch=catch(mac)[,ac(2001:2021)],sr=rec(vpa))
macFmsy=fwd(propagate(mac,nits),f=    macFtar,                   sr=rec(vpa))
pmac=plot(window(FLStocks("Original"=mac,
                          #"ICES-f"  =fwd(mac,f=    fbar( mac)[,ac(2001:2021)],sr=rec(vpa)),
                          "Fmsy"    =macFmsy,
                          "ICES-ctc"=macCtc),
          1995))+
   geom_line(aes(year,data,col=stock),
            data=transform(subset(refs,spp=="Mackerel"&ref%in%c("blim","bpa","msybtrigger")),stock=ref))+
   scale_color_manual(values=c("red","blue","green","orange","pink","purple"))+
   scale_x_continuous(breaks=c(2001,2011,2021))

pmac$data$qname=factor(pmac$data$qname,levels=c("Rec","F","Catch","SSB"))

mac=fwd(propagate(mac,nits),catch=catch(mac)[,ac(2001:2021)],sr=rec(vpa))
```


```{r, hind, fig.width=10,fig.height=6, cache=FALSE}
library(ggpubr)
p=ggarrange(pwhb+theme_bw()+  
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)),
          pher+theme_bw()+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)),
          pmac+theme_bw()+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)), 
          nrow = 1,ncol=3,
          common.legend=TRUE,
          labels = c("WHB","HER","MAC")) 
```

**Figure `r iFig=iFig+1; iFig`** Comparison of historical assessments with projections at $F_{MSY}$. 


## Projections

```{r, whbProj}
whbFtar=as.FLQuant(subset(refs,spp=="Blue whiting"&ref=="fmsy"&year>=2001)[,c("year","data")])[,-22]
whbFtar[is.na(whbFtar)]=0.18

whbFwd =prj(whb,whbFtar)
whbFwd2=prj(whb,whbFtar%=%c(whbFtar[,dim(whbFtar)[2]]))

proj=list("whb"=plot(window(FLStocks("Fmsy"=whbFwd,"Fmsy 2"=whbFwd2,"Status Quo"=whb),start=1990))+
  scale_colour_manual("Scenario",values=c("red","blue","orange"))+
  theme_bw()+
  theme(legend.position="bottom"))
```


```{r, herProj}
herFtar=as.FLQuant(subset(refs,spp=="Herring"&ref=="fmsy"&year>=2001)[,c("year","data")])[,-22]
herFtar[is.na(herFtar)]=0.25

herFwd=prj(her,herFtar)
herFwd2=prj(her,herFtar%=%c(herFtar[,dim(herFtar)[2]]))

proj[["her"]]=plot(window(FLStocks("Fmsy"=herFwd,"Fmsy 2"=herFwd2,"Status Quo"=her),start=1990))+
  scale_colour_manual("Scenario",values=c("red","blue","orange"))+
  theme_bw()+ 
  theme(legend.position="bottom")
```


```{r, macProj}
macFtar=as.FLQuant(subset(refs,spp=="Mackerel"&ref=="fmsy"&year>=2001)[,c("year","data")])[,-22]
macFtar[is.na(macFtar)]=0.22

macFwd=prj(mac,macFtar) 
macFwd2=prj(mac,macFtar%=%c(macFtar[,dim(macFtar)[2]]))
 
proj[["mac"]]=plot(window(FLStocks("Fmsy"=macFwd,"Fmsy 2"=macFwd2,"Status Quo"=mac),start=1990))+
  scale_colour_manual("Scenario",values=c("red","blue","orange"))+
  theme_bw()+
  theme(legend.position="bottom")
```


```{r, proj, fig.width=10,fig.height=6, cache=FALSE}
library(ggpubr)  
ggarrange(proj[["whb"]]+theme_bw()+  
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)),
          proj[["her"]]+theme_bw()+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)),
          proj[["mac"]]+theme_bw()+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)), 
          nrow = 1,ncol=3,
          common.legend=TRUE,
          labels = c("WHB","HER","MAC")) 
```

**Figure `r iFig=iFig+1; iFig`** Comparison of reported catch and $F_{MSY}$ projections at $F_{MSY}$. 

```{r}
whbRefs=FLQuants(dlply(subset(refs,spp=="Blue whiting"),.(ref), with, as.FLQuant(data.frame(year=year,data=data))))
herRefs=FLQuants(dlply(subset(refs,spp=="Herring"),     .(ref), with, as.FLQuant(data.frame(year=year,data=data))))
macRefs=FLQuants(dlply(subset(refs,spp=="Mackerel"),    .(ref), with, as.FLQuant(data.frame(year=year,data=data))))

save(whb,whbFtar,whbErr,whbCtc,whbFmsy,whbRefs,file=file.path(dropboxdir,"data/om/whbOM.RData"))
save(her,herFtar,herErr,herCtc,herFmsy,herRefs,file=file.path(dropboxdir,"data/om/herOM.RData"))
save(mac,macFtar,macErr,macCtc,macFmsy,macRefs,file=file.path(dropboxdir,"data/om/macOM.RData")) 
```

## Retrospective analyses

```{r, whb-retro}
retros=list("whb"=plot(window(whbRet,start=1990),metrics=list("SSB"=ssb,"F"=fbar))+
  theme_bw()+ 
  theme(legend.position="none"))
```

```{r, her-retro}
retros[["her"]]=plot(window(herRet,start=1990),metrics=list("SSB"=ssb,"F"=fbar))+
  theme_bw()+ 
  theme(legend.position="none")
```

```{r, mac-retro}
retros[["mac"]]=plot(window(macRet,start=1990),metrics=list("SSB"=ssb,"F"=fbar))+
  theme_bw()+ 
  theme(legend.position="none")
```


```{r, retro, fig.width=10,fig.height=3, cache=FALSE}
library(ggpubr)  
ggarrange(retros[["whb"]]+  
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)),
          retros[["her"]]+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)),
          retros[["mac"]]+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)), 
          nrow = 1,ncol=3,
          common.legend=TRUE,
          labels = c("WHB","HER","MAC")) 
```

**Figure `r iFig=iFig+1; iFig`** Retrospective analysis for ICES assessments. 


## Assessment Error

```{r, whb-err, fig.height=8, fig.width=8}
library(grid) 

dt=as.data.frame(rmvnorm(1000,c(1,1),cov(whbErr[-1,])))

names(dt)=c("stock","harvest")
kobePhaseMar(dt,quadcol=c("white","white","white","white"),
  xlab="F",ylab="SSB")
```

**Figure `r iFig=iFig+1; iFig`a** Blue whiting: assessment error 


```{r, her-err, fig.height=8, fig.width=8}
dt=as.data.frame(rmvnorm(1000,c(1,1),cov(herErr[-1,])))

names(dt)=c("stock","harvest")
kobePhaseMar(dt,quadcol=c("white","white","white","white"),
  xlab="F",ylab="SSB")
```

**Figure `r iFig=iFig; iFig`b** Herring: assessment error

```{r, mac-err, fig.height=8, fig.width=8}
dt=as.data.frame(rmvnorm(1000,c(1,1),cov(macErr[-1,])))

names(dt)=c("stock","harvest")
kobePhaseMar(dt,quadcol=c("white","white","white","white"),
  xlab="F",ylab="SSB")
```

**Figure `r iFig=iFig; iFig`c** Mackerel: assessment error

```{r, eval=F}
load(file.path(dropboxdir, "data/inputs/MAC/model fit.RData"))
load(file.path(dropboxdir,"data/om/mac.RData"))

value=sam2FLQuant(fit.new)
sd   =sam2FLQuant(fit.new,2)

ggplot(mcf(FLQuants("FLStock"=catch(mac),"fit"=value[["catch"]])))+geom_line(aes(year,data,col=qname))

f   =FLQuant(exp(x[["pl"]][["logF"]]),dimnames=list(age=0:7,year=1980:2022),unit="f")
f   =FLCore:::expand(f,age=0:12)
f[ac(8:12)]=f[ac(7)]

sn=FLQuant(exp(x[[2]][["logN"]]),dimnames=list(age=0:12,year=1980:2022))
s2=FLQuant(x[["sdrep"]][[7]][names(x[["sdrep"]][[7]])=="logN"],dimnames=list(age=0:12,year=1980:2022))
x[["sdrep"]][["diag.cov.random"]]

snVar=FLQuant(x[["sdrep"]][["diag.cov.random"]][names(x[["sdrep"]][[7]])=="logN"],dimnames=list(age=0:12,year=1980:2022))^0.5

vpa=mac+FLAssess:::VPA(mac)

ftar=as.FLQuant(subset(refs,spp=="Mackerel"&ref=="fmsy"&year>=2001)[,c("year","data")])[,-22]
ftar[is.na(ftar)]=0.22

plot(window(FLStocks("ICES"=mac,"VPA"=vpa,"fwd"=fwd(vpa,f=fbar(mac)[,ac(2001:2021)],sr=rec(vpa)),
                     "ftar"=fwd(mac,f=ftar[,ac(2001:2021)],sr=rec(vpa)))))

res=fwd(mac,sr=rec(mac),control=control)


mac2=mac
harvest(mac2)=f[,ac(1980:2021)]
stock.n(mac2)=stkn[,ac(1980:2021)]

sn=x[[1]][[7]][names(x[[1]][[7]])=="logN"]
```

```{r, runWhb}
stk="whb" 
source("../run/runHcr.R") 
```

```{r, runHer}
stk="her"  
source("../run/runHcr.R") 
```

```{r, runMac}
stk="mac"  
source("../run/runHcr.R")
```

```{r, smry, cache=FALSE}
source("../R/pm.R") 

library(FLCore)
library(ggplotFL)
library(ggpubr)
library(plyr)

load(file.path(dropboxdir,paste("data/runs/","whb",".RData",sep=""))) 
whb=plot(window(FLStocks(llply(sims,function(x) x[[1]]))[c(1:6,9)],start=1991))
whbY=ldply(sims, function(x) as.data.frame(pmYear(x[[1]]),drop=T))
whbI=ldply(sims, function(x) model.frame(pmIter(x[[1]])))
whbC=plot(FLQuants(llply(sims[-1],function(x) catch(window(x[[1]],start=2000,end=2021)))))+
  geom_line(aes(year,data),data=as.data.frame(catch(sims[[1]][[1]])[,ac(2000:2021)]),col="red")+facet_grid(qname~.)
whbS=plot(FLQuants(llply(sims[-1],function(x) ssb(window(x[[1]],start=2000,end=2021)))))+
  geom_line(aes(year,data),data=as.data.frame(apply(ssb(sims[[1]][[1]]),2,median)[,ac(2000:2021)]),linetype=2)+
  geom_line(aes(year,data),data=as.data.frame(refs$blim),col="red")+
  geom_line(aes(year,data),data=as.data.frame(refs$bpa), col="orange")+
  geom_line(aes(year,data),data=as.data.frame(refs$msybtrigger),col="blue")+
  facet_grid(qname~.)

load(file.path(dropboxdir,paste("data/runs/","her",".RData",sep="")))
her=plot(window(FLStocks(llply(sims,function(x) x[[1]]))[c(1:6,9)],start=1991))
herY=ldply(sims, function(x) as.data.frame(pmYear(x[[1]]),drop=T))
herI=ldply(sims, function(x) model.frame(pmIter(x[[1]])))
herC=plot(FLQuants(llply(sims[-1],function(x) catch(window(x[[1]],start=2000,end=2021)))))+
  geom_line(aes(year,data),data=as.data.frame(catch(sims[[1]][[1]])[,ac(2000:2021)]),col="red")+facet_grid(qname~.)
herS=plot(FLQuants(llply(sims[-1],function(x) ssb(window(x[[1]],start=2000,end=2021)))))+
  geom_line(aes(year,data),data=as.data.frame(apply(ssb(sims[[1]][[1]]),2,median)[,ac(2000:2021)]),linetype=2)+
  geom_line(aes(year,data),data=as.data.frame(refs$blim),col="red")+
  geom_line(aes(year,data),data=as.data.frame(refs$bpa), col="orange")+
  geom_line(aes(year,data),data=as.data.frame(refs$msybtrigger),col="blue")+
  facet_grid(qname~.)

load(file.path(dropboxdir,paste("data/runs/","mac",".RData",sep="")))
mac=plot(window(FLStocks(llply(sims,function(x) x[[1]]))[c(1:6,9)],start=1991))
macY=ldply(sims, function(x) as.data.frame(pmYear(x[[1]]),drop=T))
macI=ldply(sims, function(x) model.frame(pmIter(x[[1]]))) 
macC=plot(FLQuants(llply(sims[-1],function(x) catch(window(x[[1]],start=2000,end=2021)))))+
  geom_line(aes(year,data),data=as.data.frame(catch(sims[[1]][[1]])[,ac(2000:2021)]),col="red")+facet_grid(qname~.)
macS=plot(FLQuants(llply(sims[-1],function(x) ssb(window(x[[1]],start=2000,end=2021)))))+
  geom_line(aes(year,data),data=as.data.frame(apply(ssb(sims[[1]][[1]]),2,median)[,ac(2000:2021)]),linetype=2)+
  geom_line(aes(year,data),data=as.data.frame(refs$blim),col="red")+
  geom_line(aes(year,data),data=as.data.frame(refs$bpa), col="orange")+
  geom_line(aes(year,data),data=as.data.frame(refs$msybtrigger),col="blue")+
  facet_grid(qname~.)

save(whbY,whbI,herY,herI,macY,macI,file=file.path(dropboxdir,paste("data/results/","smry",".RData",sep="")))
```


```{r, smry-yr, fig.width=12,fig.height=6, cache=FALSE}
ggarrange(whb+theme_bw()+
  theme(panel.grid.major =element_blank(),  
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)),
          her+theme_bw()+ 
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)),
          mac+theme_bw()+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)), 
          nrow = 1,ncol=3,
          common.legend=TRUE,
          labels = c("WHB","HER","MAC"))
```

**Figure `r iFig=iFig+1; iFig`** MSEs

```{r, catch, fig.width=12,fig.height=8, cache=FALSE}
ggarrange(whbC+theme_bw()+ 
  theme(panel.grid.major =element_blank(),  
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)),
          herC+theme_bw()+ 
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)),
          macC+theme_bw()+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)), 
          nrow = 1,ncol=3,
          common.legend=TRUE,
          labels = c("WHB","HER","MAC"))
```

**Figure `r iFig=iFig+1; iFig`** Catches


```{r, ssb, fig.width=12,fig.height=8, cache=FALSE}
ggarrange(whbS+theme_bw()+ 
  theme(panel.grid.major =element_blank(),  
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)),
          herS+theme_bw()+ 
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)),
          macS+theme_bw()+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)), 
          nrow = 1,ncol=3,
          common.legend=TRUE,
          labels = c("WHB","HER","MAC"))
```

**Figure `r iFig=iFig+1; iFig`** SSB

```{r, smry-I, fig.width=12,fig.height=6, cache=FALSE}
load(file.path(dropboxdir,paste("data/results/","smry",".RData",sep=""))) 

p1=ggboxplot(subset(whbY,!.id%in%c("bbb")&qname!="rec"),y="median")+facet_grid(qname~.id,scale="free")
p2=ggboxplot(subset(herY,!.id%in%c("bbb")&qname!="rec"),y="median")+facet_grid(qname~.id,scale="free")
p3=ggboxplot(subset(macY,!.id%in%c("bbb")&qname!="rec"),y="median")+facet_grid(qname~.id,scale="free")

ggarrange(p1+theme_bw()+   
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)),
          p2+theme_bw()+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)),
          p3+theme_bw()+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)), 
          nrow = 1,ncol=3,
          common.legend=TRUE,
          labels = c("WHB","HER","MAC"))
```

```{r, fig.width=12,fig.height=6, cache=FALSE}
library(reshape)
p1=ggboxplot(melt(whbI[,-5],id=".id"),y="value")+facet_grid(variable~.id,scale="free")
p2=ggboxplot(melt(herI[,-5],id=".id"),y="value")+facet_grid(variable~.id,scale="free")
p3=ggboxplot(melt(macI[,-5],id=".id"),y="value")+facet_grid(variable~.id,scale="free")
 
ggarrange(p1+theme_bw()+   
  theme(panel.grid.major =element_blank(), 
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)),
          p2+theme_bw()+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)),
          p3+theme_bw()+
  theme(panel.grid.major =element_blank(),
        axis.ticks       =element_blank(),
        axis.text.y      =element_blank(),
        panel.border     =element_rect(linetype = 1, colour="black", fill=NA)), 
          nrow = 1,ncol=3,
          common.legend=TRUE,
          labels = c("WHB","HER","MAC"))
```

# Funding

# References
